Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-10-24 numerics_paper/version2/numerical_chj.tex
Add modification based on the comments from the 1st reviwer

Using this Riemann solver (within the second-order Lax-Wendroff-LeVeque 
finite volume scheme \cite{leveque1997wave, leveque2002finite}) supresses the formation of carbuncles 
while maintaining an accuracy similar to that of Roe solver.  
Based on our numerical experiments, using Rusanov's solver does not lead to the 
slowly-moving shock anomaly. Our blended solver inherits the same property.

>>>>

Using this Riemann solver (within the second-order Lax-Wendroff-LeVeque 
finite volume scheme \cite{leveque1997wave, leveque2002finite}) supresses the formation of carbuncles 
while maintaining an accuracy similar to that of Roe solver.  
Based on our numerical experiments, 
{\color{red} the Rusanov's solver does not perturb the location of steady shocks.} 
Our blended solver inherits the same property.
